---
title: "README"
author: "Thomas Pin"
date: "29/02/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(knitr)

course_key <- tibble(`Course Number` = c(563, 524, 553, 574),
       `Course Name` = c("Unsupervised Learning", "Collaborative Software Development", "Statistical Inference and Computation II", "Spatial and Temporal Models"))
```

# UBC MDS block 5 homework

A GitHub repository that serves 2 purposes:

1. a learning space to explore and practice using GitHub issues in milestones and Project boards
2. a homework organizer for UBC MDS students for their 5th block in the program

## Course Key

```{r, echo=FALSE}
kable(course_key)
```

## Usage

1. Import this repository to obtain a copy of it for yourself (do not fork it).
2. Create a remote branch named create (this will use GitHub Actions to create 19 issues for you in your copy of this repository).
3. Create 5 milestones, named week 1 through to week 5, and group the relevant issue to each milestone.
4. Create a project board named block 5. Put the issues in appropriate columns.

